%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Module:    ZzTeX Help Text
%
% Synopsis:  This file contains the help text for each error and
%            warning signaled by ZzTeX.
%
% Author:    Paul C. Anagnostopoulos
% Created:   3 July 1990
%
% Copyright 1989--2020 by Paul C. Anagnostopoulos
% under The MIT License (opensource.org/licenses/MIT)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\long\def \definehelp #1#2{%                    {help-id}{text}
  \withname\gdef{\=zH:#1}{#2}}


\definehelp{adjheads}{
  You must eliminate the inter-row space between two adjacent rows_
  of column heads. This is done with the \closeuprows command.}

\definehelp{altinv}{
  The design alternative named above was specified with an_
  invalid value in a \designalternative command.}

\definehelp{altreq}{
  The design alternative named above must be specifed with a_
  \designalternative command preceding the \loaddesign in_
  your root file. There is no default.}

\definehelp{artpos}{
  The \art command is in the wrong position relative to the_
  \caption command.}

\definehelp{blkcantnest}{
  The file contains an occurence of the first block mentioned above_
  nested inside the second block. This is not allowed.}

\definehelp{blkinvnest}{
  A command to end a block is not properly associated with the command_
  to begin the block. For example, an \endtext is matched with a \list._
  All blocks must be properly nested.}

\definehelp{blkmustend}{
  The file contains an occurence of the block ending command_
  mentioned first, but it is not preceded by the block starting_
  command mentioned second. Each block must have a starting command.}

\definehelp{blkmustnest}{
  The file contains an occurence of the first block mentioned above,_
  but it is not nested inside the second block. The first block_
  must be nested in the second.}

\definehelp{cananchor}{
  The object anchor specified mentioned above is invalid._
  Valid anchors are 'a' -- 'h'.}

\definehelp{celldecpt}{
  The picutre for this decimal-aligned cell did not include a decimal_
  point, but the number to be typeset does. You must include a_
  decimal point in the template or remove it from the number.}

\definehelp{citelet}{
  It appears that you have used \let to define a \citexxx command_
  in the design file. This done not work; use \def instead.}

\definehelp{desjunk}{
  The design file named above contains some paragraph (horizontal mode)_
  text that should not be there.__
  You probably left a percent sign off a comment.}

\definehelp{divnotexist}{
  The division specified in the message is not included with a_
  \division command in the root file.}

\definehelp{dupart}{
  The art file named above is used more than once in the book.__
  If a figure really is used more than once, you must copy it with
  another name and change one of the \art commands.}

\definehelp{dupreg}{
  The register named above has already been defined with another_
  \definexxx command.}

\definehelp{divortah}{
  The \overridetextareaheight command has been used to override the_
  text area height, but the override crosses from one division to the next.__
  If you continue from the warning, the override will be cancelled.}

\definehelp{empshape}{
  The \shapepar command must be specified with at least one pair of_
  indent/width arguments. You have specified one with no arguments.}

\definehelp{hereonlybot}{
  ZzTeX cannot position the float `here' because there is already_
  a float positioned at the bottom of the page. Floats must be_
  positioned in order.}

\definehelp{invindexlvl}{
  The level specified in an indexing command must be 1, 2, or 3.}

\definehelp{invoper}{
  The operator shown above is not valid in the expression argument_
  of the \calculate command.}

\definehelp{invsubpart}{
  The subpart argument to \markinfo(upcased) must be 1 or 2._
  You have specified the invalid subpart number shown above.}

\definehelp{locattr}{
  The attributes of the index locator are not valid. You must specify_
  at least one of \page or \text.}

\definehelp{missbb}{
  The specified art file does not have a bounding box comment, so_
  ZzTeX cannot determine the size of the art.}

\definehelp{misset}{
  A tabular column template must begin with \set, so that the column
  type will be correctly interpreted.}

\definehelp{misstah}{
  The value of \textareaheight must be established by the document_
  design macro before \calculatetypeareaheight can be used.__
  You can set it directly or calculate it with \calculatetextareaheight.}

\definehelp{misstopskip}{
  The value of \topskip must be established by the document design_
  macro before \calculatetextareaheight can be used.}

\definehelp{misstrim}{
  The values of \trimwidth and \trimheight must be established by the_
  document design macro before \calculateoffsets can be used}

\definehelp{needheads}{
  The \tabheadrule and \skipbelowcolhead commands require that the_
  previous row is a row of heads.}

\definehelp{negtabvsp}{
  A negative \tabvspace will not work; it produces no spacing at all._
  You must use \tabcloseup.}

\definehelp{noartfile}{
  You have requested the art file named above for an \art block,_
  but the file does not exist.__
  If you continue from this warning, the art space will be framed_
  with corner marks and contain the name of the missing file.}

\definehelp{nobblfile}{
  You have requested a bibliography list with the \biblio command,_
  but there is no bibliography item file.__
  If you continue from this warning, the bibliography list will not_
  be typeset. You must first run BibTeX to produce the item file.}
  
\definehelp{nodesfile}{
  The design file named above is required for this book, but it_
  does not exist.__
  You may have misspelled the name of the design file in the_
  \loaddesign command. If not, the design file must be created.}

\definehelp{nodesign}{
  The file contains a use of the block named above, but the_
  book's design file does not contain a design macro_
  for the block.__
  It's possible you have misspelled the name of the block_
  or its type (if any). If not, a design macro must be_
  added to the design file.}

\definehelp{nodivs}{
  The \setdivisions command must specify one or more divisions to set.}

\definehelp{noend}{
  Do not use the \end command in ZzTeX. The root file is terminated_
  with the \enddocument command.__
  If you are trying to end a block, such as a \list block, you must_
  use the corresponding ending command, such as \endlist.}

\definehelp{nofloatpos}{
  The \position parameter for a float does not specify any_
  page positions for the float. The page positions are \alone,_
  \bottom, \here, \separate, and \top. Without a page_
  position, the float cannot be placed on the page.__
  This error could be due to a missing position in the design file._
  Or, you may have specified the \position parameter in a \with_
  command on the float block and forgotten to include any of the_
  page positions.__
  If you continue, the float will be placed alone on a page. This_
  message may appear again for the same float.}

\definehelp{nofontset}{
  The file has requested a font of the size and style mentioned above._
  No font has been set for this size/style in the book's design file.__
  You may have misspelled the name of the size or style. If not,_
  the appropriate font must be established in the design file.}

\definehelp{noheadfoot}{
  The design file does not contain a definition for the header_
  or footer format specified in the message. These definitions_
  must be included in the design file.}

\definehelp{noinclfile}{
  The file mentioned above has been requested with an \include or_
  \division command, but it does not exist.__
  You may have misspelled the name of the file. If not, you must_
  create it before processing the book again.__
  If you continue from this error, ZzTeX will prompt you for another_
  file name.}

\definehelp{nomarks}{
  The \markinfo command is being used to format a running head_
  or foot, but no mark information has been provided for the_
  current page.__
  This only happens at the beginning of a book, before the first_
  chapter or quasichapter. You may have set running heads and_
  feet with \setrunners before the first chapter or quasichapter.}

\definehelp{nomnpos}{
  The \position parameter for a margin note does not specify any_
  horizontal position for the float. The positions are \leftmargin,_
  \rightmargin, and \outsidemargin.}

\definehelp{noreftitle}{
  The use of the \reftitle command has been disabled in the_
  design file with the \allowreftitle document parameter.__
  If you did not intend to use the \reftitle command, you must_
  remove it from the file. If you need to use it, then modify_
  the design file appropriately.}

\definehelp{noregsleft}{
  All of the available registers of the type specified in the_
  message have been allocated for use, but a request for another_
  such register has been made.}

\definehelp{norelstyle}{
  You have requested a type style related to the current style,_
  but no such relation has been established. For example, the_
  current style is \tt and you want to emphasize text with the_
  \emph command, but no style for emphasizing monospaced text_
  has been established.__
  Use the \definestylerelation command to establish the appropriate_
  relationship.}

\definehelp{notaginfo}{
  A \tag command has been specified in the current block, but_
  the composite number and title has not been established yet.}

\definehelp{notindexing}{
  ZzTeX has encountered an indexing command (e.g., \xpage), but_
  you have not included a \produceindex command in the root file._
  At least one \produceindex command is required if the files contain_
  indexing commands.__
  If you continue from the warning, the index entries will be written_
  to the log file.}

\definehelp{notps}{
  The feature show above is only available when you are producing_
  PostScript output. It requires PostScript capabilities.}

\definehelp{nowith}{
  The \with modifier is not allowed on the command specified in the_
  message. You must remove the \with modifier.__
  If you continue from this warning, the \with will be ignored._
  If you used \with on an \item command, use it on the \list_
  command instead (it will apply to the entire list).}

\definehelp{obsolete}{
  The command named above is obsolete in this version of ZzTeX.}

\definehelp{openblock}{
  One or more blocks are in progress at the end of a chapter,_
  appendix, or quasichapter. The names of the blocks are listed_
  in messages preceding this warning.__
  The problem is caused by missing \endxxx commands. For example,_
  you have coded a list but forgotten the \endlist command. You_
  will probably see the message `(\end occurred inside a group at_
  level 1)' at the end of the log.}

\definehelp{overortah}{
  The \overridetextareaheight command has been used to override the_
  text area height, but a previous override is still in progress.__
  If you continue from the warning, the first command will be cancelled_
  and the second one will take effect. However, the height of the current_
  page may be incorrect.}

\definehelp{pagepar}{
  A command has been used to request a page break in the middle of_
  a paragraph.__
  You must terminate the paragraph before using the command.}

\definehelp{plaintex}{
  The Plain TeX command shown below cannot be used in ZzTeX.}

\definehelp{scinmath}{
  You have tried to use a special character that is not available_
  in math mode.__
  If you need it, use it in a \text command.}

\definehelp{setminus}{
  When using the MathTime fonts, it is better to use \setdiff than_
  \setminus. If you really want to use \setminus, you will need_
  to define it in the design file.}

\definehelp{spectah}{
  The design spec's text area height, as specified by \spectextareaheight,_
  differs from the calculated text area height by more than 3 points._
  You should contact the designer about this.}

\definehelp{skipab}{
  A sequence of elements in the book has resulted in a request_
  for a `skip below an element' followed immediately by a_
  `skip above an element'. Such a sequence is invalid.__
  There is probably an error in the design file.}

\definehelp{toomanyflt}{
  There are more than the specified number of floats pending for_
  page makeup. A float is pending for makeup when it has been_
  encountered in a file but not yet placed on a page of the book.__
  You must reorganize the file so that the floats are more spread_
  out in the text, this giving ZzTeX an opportunity to place the_
  floats on pages as soon as they are encountered.}

\definehelp{undefat}{
  The atsign command sequence specified above has not been defined_
  in this block. It must be defined before you can use it.__
  Use the \defineatsigncommand command to define the command.}

\definehelp{undefflt}{
  The float type specified above has not been defined. It must be_
  defined before you can use it.__
  Use the \definefloattype command to define the float.}

\definehelp{unimpl}{
  The ZzTeX feature mentioned above is not yet implemented.__
  Please contact Windfall Software if you need the feature.}

\definehelp{lockedfont}{
  The font specified above is locked, which means it was not correctly_
  installed with ZzTFM.__
  Please contact Windfall Software to determine a remedy.}

\definehelp{varmod}{
  A variant definition must include between 1 and 8 modifier commands.__
  Modifier commands are specified as a comma-separated list in the third_
  argument to \definevariant.}

\definehelp{xtran}{
  An error flag from the XTran H converter is still present in this_
  file. The flag message is shown in the above error message.__
  You should fix the error flagged by XTran and remove the flag_
  message from the source file.}

\definehelp{zztran}{
  An error flag from the ZzTran converter is still present in this_
  file. The flag message is shown in the above error message.__
  You should fix the error flagged by ZzTran and remove the flag_
  message from the source file.}